\textbf{Autoreduction - an automated data reduction system for beam instruments}

### 2016-09-22 Documentation/paper/paper.tex
Updating paper, removing unused files.

\documentclass[twocolumn]{article}
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdftitle={Autoreduction - an automated data reduction system for beam instruments},
            pdfauthor={J. R. Corderoy - ISIS Facility, Rutherford Appleton Laboratory - jrc91@cam.ac.uk},
            pdfborder={0 0 0},
            breaklinks=true}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}

\title{Autoreduction - an automated data reduction system for beam instruments}
\author{J. R. Corderoy - ISIS Facility, Rutherford Appleton Laboratory -
jrc91@cam.ac.uk}
\date{23/09/2015}

@@

@@

@@

\begin{enumerate}
\item
  Automate the reduction of data from beam instruments, using scripts
  provided by instrument scientists.
\item
  Show the status of reduction on runs, as well as the results and
  locations of reduced data, to users.
\item
  Allow instrument scientists to set the parameters used for reduction,
  in advance and retroactively.
\item
  Allow users and instrument scientists to see what script, with which
  parameters, was used to reduce a run.
\item
  Allow users and instrument scientists to modify the parameters used
  for a run, and re-run reduction using new parameters or scripts.
\end{enumerate}

@@

\begin{enumerate}
\item
  Limit access to the system to ensure that only staff and scientists
  can access runs and instruments.
\item
  Utilise existing authentication systems to validate identities and
  permissions for (1).
\item
  Allow scalability for processing large amounts of data in a timely
  manner.
\item
  Integrate with ICAT \cite{icat} -- the scientific metadata catalogue in use
  at ISIS .
\end{enumerate}

@@

\begin{enumerate}
\item
  A listener for new jobs
\item
  The state database \& coordinator
\item
  Workers for reduction processing
\end{enumerate}

@@

\begin{figure*}[!htbp]
\includegraphics{system.png}
\caption{How the autoreduction system fits into the ISIS workflow.}
\end{figure*}

@@

Apache ActiveMQ \cite{activemq} is used as the message queueing system, with
message contents as JSON-formatted objects. The intention of the message
is conveyed by which queue it's placed in, rather than a field in the
message itself. Runs can be `scheduled' simply by using ActiveMQ's
scheduled delay feature, which allows a message to be delivered a given
time after it's been pushed to the queue.

@@

A node keeps track of the status of runs in a local SQL database. This
server hosts a Python service responsible for listening on \emph{Data
Ready}, to create new runs and then dispatch them to \emph{Reduction
Pending}. It manages variables for reduction, and selects the correct
set for the run. The same server is responsible for serving the
Python/Django web app. The database is therefore accessed through
Django's object interface, and reduction runs, etc., are tracked as
Django objects.

@@

Users log in via the ISIS User Office -- using their federated
credentials -- and their level of access is then governed by ICAT's
information on the experiments and instruments they should be able to
see. A searchable index of runs is displayed on the front page, sorted
by instrument, experiment and run number, showing their reduction
status. Runs, experiments and instruments displayed here have links to
their summary pages.

@@

The system is deployed at ISIS, in limited use. The frontend node,
serving the message queue as well as managing the state and web app, is
a Windows Server system running on a Hyper-V cluster; it serves the web
app using Microsoft's Internet Information Services (IIS) and FastCGI.
There is one reduction node, running Red Hat Enterprise Linux on a
dedicated Dell PowerEdge R820 server -- reducing large amounts of data
is very CPU-intensive.

@@

\begin{thebibliography}{9}
\bibitem{icat}
    The ICAT Collaboration,
    \emph{The Icat Project.},
    2014,
    \href{https://doi.org/10.5286/SOFTWARE/ICAT}{10.5286/SOFTWARE/ICAT}.

\bibitem{activemq}
    Apache Software Foundation,
    \emph{Apache Activemq},
    \url{http://http://activemq.apache.org/},
\end{thebibliography}
\end{document}

>>>>

\documentclass[twocolumn]{article}

\usepackage[unicode=true]{hyperref}
\usepackage{enumitem}
\usepackage{graphicx,grffile}

\title{\textbf{Autoreduction - an automated data reduction system for beam instruments}}
\author{J. R. Corderoy\\
ISIS Facility, Rutherford Appleton Laboratory\\
Email: jrc91@cam.ac.uk}
\date{23/09/2015}

@@

A key step for users of large research facilities is the routine
processing of instrument data before use. Autoreduction is a software
system designed to automate this process, integrated with other
pre-existing facility systems and software packages, and provide
an interface for users to control it.

@@

High-energy particle facilities, such as the ISIS Neutron and Muon
Facility, allow users in academic and industrial research
to perform experiments using instruments set up to use high-energy
particle beams. Common to most instruments is the need to process -- 
`reduce' -- raw data collected from an instrument into a usable dataset.

The goal for the autoreduction system is to provide a useful automation
step in this process. It allows data coming off an instrument to be
automatically reduced using a dedicated software package such as 
Mantid\cite{mantid}, while lending transparency to the process and
letting users control it through a straightforward web interface.

Presented below is an overview of the motivation and design of the system,
its use and interface, and its current status in production at ISIS.

@@

\begin{enumerate}[noitemsep]
\item
  Automate the reduction of data from beam instruments, using scripts
  provided by instrument scientists.
\item
  Show the status of reduction on runs, as well as the results and
  locations of reduced data, to users.
\item
  Allow instrument scientists to set the parameters used for reduction,
  in advance and retroactively.
\item
  Allow users and instrument scientists to see what script, with which
  parameters, was used to reduce a run.
\item
  Allow users and instrument scientists to modify the parameters used
  for a run, and re-run reduction using new parameters or scripts.
\end{enumerate}

@@

\begin{enumerate}[noitemsep,resume]
\item
  Limit access to the system to ensure that only staff and scientists
  can access runs and instruments.
\item
  Utilise existing authentication systems to validate identities and
  permissions for (1).
\item
  Allow scalability for processing large amounts of data in a timely
  manner.
\item
  Integrate with ICAT\cite{icat} -- the scientific metadata catalogue in use
  at ISIS.
\end{enumerate}

@@

\begin{itemize}[noitemsep]
\item
  A listener for new jobs
\item
  The state database \& coordinator
\item
  Workers for reduction processing
\end{itemize}

@@

\begin{figure*}
\centering\includegraphics[width=1.15\linewidth,angle=90,origin=c]{system.png}
\caption{How the autoreduction system fits into the ISIS workflow.}
\end{figure*}

@@

Apache ActiveMQ\cite{activemq} is used as the message queueing system, with
message contents as JSON-formatted objects. The intention of the message
is conveyed by which queue it's placed in, rather than a field in the
message itself. Runs can be `scheduled' simply by using ActiveMQ's
scheduled delay feature, which allows a message to be delivered a given
time after it's been pushed to the queue.

@@

A node keeps track of the status of runs in a local SQL database. This
server hosts a Python service responsible for listening on \emph{Data
Ready}, to create new runs and then dispatch them to \emph{Reduction
Pending}. It manages variables for reduction, and selects the correct
set for the run. The same server is responsible for serving the
Python/Django\cite{django} web app. The database is therefore accessed through
Django's object interface, and reduction runs, etc., are tracked as
Django objects.

@@

Users log in via the ISIS User Office system -- using credentials 
granted for facility-wide use -- and their level of access is then 
governed by ICAT's information on the experiments and instruments they 
should be able to see. A searchable index of runs is displayed on the front page, sorted
by instrument, experiment and run number, showing their reduction
status. Runs, experiments and instruments displayed here have links to
their summary pages.

@@

The system is deployed at ISIS, in limited use. The frontend node,
serving the message queue as well as managing the state and web app, is
a Windows Server system running on a Hyper-V\cite{hyper-v} virtualisation
cluster; it serves the web app using Microsoft's Internet Information
Services (IIS)\cite{iis} and FastCGI\cite{fcgi}. There is one reduction node, 
running Red Hat Enterprise Linux 7\cite{rhel} on a dedicated server -- 
reducing large amounts of data is very CPU-intensive.

@@

The autoreduction system offers a convenient way of automating data reduction
on beamline instruments. It uses a scalable architecture to allow prompt
reduction of data from a large number of instruments, and utilises a web app
frontend to allow users to control the reduction process manually and verify
that the correct reduction was run.

The system is currently in limited use at ISIS, with more instrument scientists
interested in using it. The source code can be found on GitHub\cite{source}.

\begin{thebibliography}{99}
\bibitem{mantid}
    O. Arnold, et al.,
    \emph{Mantid -- Data analysis and visualization package for neutron scattering and $\mu$SR experiments},
    Nuclear Instruments and Methods in Physics Research Section A, Volume 764, 11 November 2014, Pages 156-166,
    \href{http://dx.doi.org/10.1016/j.nima.2014.07.029}{10.1016/j.nima.2014.07.029}.

\bibitem{icat}
    The ICAT Collaboration,
    \emph{The Icat Project.},
    2014,
    \href{https://doi.org/10.5286/SOFTWARE/ICAT}{10.5286/software/icat}.

\bibitem{activemq}
    Apache Software Foundation,
    \emph{Apache Activemq},
    \url{http://activemq.apache.org/}.

\bibitem{django}
    Django Software Foundation,
    \emph{Django},
    \url{https://www.djangoproject.com/}.

\bibitem{hyper-v}
    Microsoft Corporation,
    \emph{Hyper-V},
    \url{https://technet.microsoft.com/en-us/library/mt169373.aspx}.

\bibitem{iis}
    Microsoft Corporation,
    \emph{IIS},
    \url{http://www.iis.net/}.

\bibitem{fcgi}
    \emph{FastCGI},
    \url{https://github.com/FastCGI-Archives/FastCGI.com}.

\bibitem{rhel}
    Red Hat, Inc,
    \emph{Red Hat Enterprise Linux},
    \url{https://www.redhat.com/en/technologies/linux-platforms/enterprise-linux}.

\bibitem{source}
    \emph{Autoreduction repository},
    \url{https://github.com/mantidproject/autoreduce}.

\end{thebibliography}
\end{document}
